---
title: "Data Types & Structures"
output: html_document
---

# Your Turn 1 

Q1. Create an object called `x` that is assigned the number 8. 

```{r}

```

Q2. Create an object called `y` that is a sequence of numbers from 2 to 16, by 2. (Replace the `___` with your code.)

```{r}
y <- seq(from = ___, to = ___, by = ___)
```

Q3. Add `x` and `y`. What happens? 

```{r}

```

# Your Turn 2

Q1. Create an object called `a` that is just the letter "a" and an object `x` that is assigned the number 8. Add `a` to `x`. What happens?

```{r}

```

Q2. Create a vector called `b` that is just the number 8 in quotes. Add `b` to `x` (from above). What happens?

```{r}

```


Q3. Find some way to add `b` to `x`. (*Hint*: Don't forget about coercion.)

```{r}

```

# Your Turn 3

Q1. Create a vector called `named` that includes the numbers 1 to 5. Name the values "a", "b", "c", "d", and "e" (in order). 

```{r}
named <- c(___)
```

Q2. Print the first element using numerical indexing and the last element using name indexing.

```{r}

```

Q3. Change the  third element of `named` to the value 21 and then show your results.

```{r}

```

# Your Turn 4

1. Create a list like mine that is made up of `name`, `height`, and `ice_cream`, but corresponds to information about you. Make sure you enter two types of icecream data (because who could choose?!).

```{r}
___ <- list(___)
```


2. Index your list to print only your name.

```{r}

```

# Your Turn 5

1. Make a data frame, called `df_2`, that has 3 columns as shown below. After you create it, check the structure.

    `c1` = c(1, 2, 3) <br>
    `c2` = c(2, 4, 6) <br>
    `c3` = c("a", "b", "c")

```{r}
df_2 <- data.frame(___)

___(df_2)
```

2. Add a fourth column, `c4`, which is the first and second columns multiplied together.

```{r}
df_2$c4 <- ___
```

3. Try to add the first and second rows together. What happens? Why?

```{r}
___ + ___
```

