---
title: "Wrangling Data with {dplyr}"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse) # if you have never used the `{tidyverse}` package before, you will need to install it using `install.packages("tidyverse")`.
```

# Your Turn 1

Q1. Convert the data frame `mtcars` to a tibble and assign the resulting object to `data`. *Note.* The data frame `mtcars` is automatically loaded in R; you don't have to install it separately.

```{r}
data <- tibble(___)
```

Q2. Filter `data` for cars that have 4 `cyl`. Arrange the resulting observations by descending order of `mpg`.

```{r}
data %>% 
  filter(___) %>% 
  arrange(___)
```

Q3. Filter `data` for cars that have `disp`s greater than or equal to 350, `hp`s greater than or equal to 200, and `qsec`s less than or equal to 17. 

```{r}
data %>% 
  filter(___)
```

Q4. Filter `data` for cars that have `carb`s equal to 4 or `cyl`s equal to 4. Assign the result to an object called `data_filtered`.

```{r}
data_filtered <- data %>% 
  filter(___)

data_filtered
```

# Your Turn 2

Q1. In `data`, select only the variables `mpg` and `hp`. 

```{r}
data %>% 
  select(___)
```

Q2. As we did with indexing in base R, you can use the minus sign (`-`) to "de-select" columns. Keep everything in `data` except `vs`.

```{r}
data %>% 
  select(___)
```

Q3. Use `mutate()` to convert `cyl` from type "double" to type "factor". *Hint:* You might want to look up the function `as.factor()`.

```{r}
data %>% 
  mutate(___)
```

# Your Turn 3

Q1. From `data`, get the mean `hp` for each of the different `cyl` values.

```{r}
data %>% 
  group_by(___) %>% 
  summarize(___ = mean(___))
```

Q2. Now get the mean `hp` for each unique combination of `cyl` and `gear` and arrange the resulting rows by descending order of `hp`. Which combination of `cyl` and `gear` had the greatest `hp`?

```{r}
data %>% 
  group_by(___, ___) %>% 
  summarize(___ = mean(___)) %>% 
  arrange(desc(___))
```
